---
title: "Visualization & Model Comparison"
author: "Dani Cosme & Rich Lopez"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = FALSE, fig.path = "figs/prediction/")
```

# load packages
```{r}
library(tidyverse)
library(knitr)
```

# define palettes
```{r}
pal_control = c("#2E86B4", "#F2B827")
pal_outcome = wesanderson::wes_palette("Zissou1", 3, "continuous")
pal_condition = wesanderson::wes_palette("Zissou1", 6, "continuous")
pal_condition8 = wesanderson::wes_palette("Zissou1", 16, "continuous")
pal_condition8 = c(pal_condition8[1], pal_condition8[3],
                  pal_condition8[14], pal_condition8[5],
                  pal_condition8[15], pal_condition8[16],
                  pal_condition8[9], pal_condition8[12])
```

# source data
* Note that % fat variable was incorrect in 2012_FDES --> replaced it with the data from the EMA dataframe

```{r, cache=TRUE}
source("load_data.R")

ind_diffs = ind_diffs %>%
  mutate(bmi_z = as.numeric(scale(bmi)),
         fat_z = as.numeric(scale(fat)))
```

# standardize brain data
* Windsorizing observations +/- 3 SD from the mean to 3 --> otherwise we lose these subs in the SCA analyses  
* Z-score within ROI and session for ROIs  
* Z-score within map, test (association or uniformity), mask (masked or unmasked) and session for PEVs  

```{r}
# roi distributions
betas %>%
  filter(session == "all") %>%
  select(subjectID, con, condition, control, roi, process, meanPE) %>%
  unique() %>%
  filter(!is.na(roi)) %>%
  ggplot(aes(meanPE, fill = roi)) +
  geom_density(color = NA) +
  facet_wrap(~roi, ncol = 4) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

# dot product distribution
dots %>%
  filter(session == "all") %>%
  select(subjectID, con, condition, control, process, test, dotProduct) %>%
  unique() %>%
  ggplot(aes(dotProduct, fill = test)) +
  geom_density(color = NA) +
  facet_wrap(~process, ncol = 3, scales = "free") +
  theme_minimal(base_size = 14) +
  theme(legend.position = c(.85, .2))

dots %>%
  filter(session == "all") %>%
  select(subjectID, con, condition, control, process, test, dotProduct, mask) %>%
  unique() %>%
  ggplot(aes(dotProduct, fill = mask, alpha = .5)) +
  geom_density(color = NA) +
  facet_wrap(~process, ncol = 3, scales = "free") +
  theme_minimal(base_size = 14) +
  theme(legend.position = c(.85, .2))

# standardize and winsorize
betas_std = betas %>%
  group_by(roi, session) %>%
  mutate(meanPE_std = scale(meanPE, center = TRUE, scale = TRUE),
         outlier = ifelse(meanPE_std > 3, "yes",
                   ifelse(meanPE_std < -3, "yes", "no")),
         meanPE_std = ifelse(meanPE_std > 3, 3,
                      ifelse(meanPE_std < -3, -3, meanPE_std))) %>%
  ungroup()

dots_std = dots %>%
  group_by(map, test, mask, session) %>%
  mutate(dotProduct_std = scale(dotProduct, center = TRUE, scale = TRUE),
         outlier = ifelse(dotProduct_std > 3, "yes",
                   ifelse(dotProduct_std < -3, "yes", "no")),
         dotProduct_std = ifelse(dotProduct_std > 3, 3,
                          ifelse(dotProduct_std < -3, -3, dotProduct_std))) %>%
  ungroup()

```

## summarize outliers
```{r}
# summarize
betas_std %>%
  filter(session == "all") %>%
  group_by(outlier) %>%
  summarize(n = n()) %>%
  spread(outlier, n) %>%
  mutate(percent = round((yes / (yes + no)) * 100, 2))

dots_std %>%
  filter(session == "all") %>%
  group_by(outlier, test, mask) %>%
  summarize(n = n()) %>%
  spread(outlier, n) %>%
  mutate(percent = round((yes / (yes + no)) * 100, 2))

# remove outlier column
betas_std = betas_std %>%
  select(-outlier)

dots_std = dots_std %>%
  select(-outlier)
```

# merge data
```{r}
dataset = full_join(betas_std, dots_std, by = c("subjectID", "con", "process", "condition", "control", "session")) %>%
  mutate(subjectID = as.character(subjectID)) %>%
  left_join(., ind_diffs, by = "subjectID") %>%
  ungroup() %>%
  mutate(subjectID = as.factor(subjectID),
         condition = as.factor(condition),
         control = as.factor(control),
         roi = as.factor(roi),
         process = as.factor(process),
         test = as.factor(test))

saveRDS(dataset, "full_dataset.RDS")
saveRDS(betas_std, "betas_dataset.RDS")
saveRDS(dots_std, "dots_dataset.RDS")
```

## tidy data for plotting
* Select cons generated across all sessions  
* Calculate mean across ROIs within each psychological process  
* Calculate balance score ROI = cognitive control - reward  

```{r}
dots_plot = dots_std %>%
  filter(mask == "unmasked") %>%
  filter(session == "all") %>%
  select(-c(map, con, mask, session, dotProduct)) %>%
  left_join(., ind_diffs) %>%
  select(-c(sample, DBIC_ID, age, gender))

betas_plot = betas_std %>%
  group_by(subjectID, process, condition, control) %>%
  mutate(meanProcessPEstd = mean(meanPE_std, na.rm = TRUE)) %>%
  select(-c(con, xyz, roi, meanPE, sdPE, meanPE_std)) %>%
  unique() %>%
  spread(process, meanProcessPEstd) %>%
  mutate(balance = cognitive_control - reward) %>%
  gather(process, meanProcessPEstd, cognitive_control, reward, value, balance) %>%
  filter(session == "all") %>%
  select(-c(session)) %>%
  left_join(., ind_diffs) %>%
  select(-c(sample, DBIC_ID, age, gender)) %>%
  ungroup()

combined_plot = dots_plot %>%
  rename("value_std" = dotProduct_std) %>%
  mutate(test = ifelse(process == "craving_regulation", "neural signature", test)) %>%
  select(subjectID, process, test, condition, control, value_std, fat, bmi) %>%
  bind_rows(betas_plot %>%
              rename("value_std" = meanProcessPEstd) %>%
              mutate(test = "ROI") %>%
              select(-contains("_z")))
```

## tidy data for modeling
```{r}
ema_tidy = ema %>%
  select(subjectID, desire_pres0.prop, desire_str.m, goal_conf.m, resist.m, enact_prop, amount_Recoded.m, hunger.m) %>%
  unique() %>%
  mutate(enact_prop_z = as.numeric(scale(enact_prop)))

model_data = dataset %>%
  filter(test == "association" & mask == "unmasked" & session == "all" & control == "nature" & condition == "food") %>%
  unique() %>%
  group_by(process, subjectID) %>%
  mutate(meanProcessPEstd = mean(meanPE_std, na.rm = TRUE),
         processPE = paste0(process, "_ROI"),
         processPEV = paste0(process, "_PEV")) %>%
  ungroup() %>%
  select(-c(xyz, meanPE, meanPE_std, sdPE, dotProduct, map, process)) %>%
  spread(processPEV, dotProduct_std) %>%
  spread(processPE, meanProcessPEstd) %>%
  group_by(subjectID) %>%
  fill(contains("PEV"), .direction = "down") %>%
  fill(contains("PEV"), .direction = "up") %>%
  fill(contains("ROI"), .direction = "down") %>%
  fill(contains("ROI"), .direction = "up") %>%
  select(-c(roi, craving_ROI, craving_regulation_ROI, test, age, gender, mask)) %>%
  unique() %>%
  mutate(balance_ROI = cognitive_control_ROI - reward_ROI)

model_data_bmi = model_data %>%
  select(-contains("fat")) %>%
  na.omit()

model_data_fat = model_data %>%
  select(-contains("bmi")) %>%
  na.omit()

model_data_ema = model_data %>%
  select(-contains("fat"), -contains("bmi")) %>%
  right_join(., ema_tidy, by = "subjectID") %>%
  na.omit()
```

# visualize
### DVs
```{r, fig.width=6, fig.height=4}
# source raincloud plot
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

# plot
model_data %>%
  left_join(., ema_tidy, by = "subjectID") %>%
  filter(!is.na(subjectID)) %>%
  select(subjectID, bmi, fat, enact_prop) %>%
  rename("BMI" = bmi,
         "body fat percentage" = fat,
         "enactment" = enact_prop) %>%
  gather(var, val, -subjectID) %>%
  ggplot(aes("", val, fill = var)) +
    geom_flat_violin(position = position_nudge(x = .1, y = 0), color = FALSE) +
    geom_boxplot(width = .1, outlier.shape = NA) +
    geom_point(position = position_jitter(width = .05), size = .5, alpha = .5) +
    facet_wrap(~var, scales = "free") +
    scale_fill_manual(values = pal_outcome) +
    scale_x_discrete(expand = c(.1, 0)) +
    coord_flip() +
    labs(y = "\nvalue", x = "") +
    theme_minimal(base_size = 14) +
    theme(legend.position = "none")
```

### combined
```{r, fig.width=10, fig.height=10}
combined_plot %>%
  filter(!process == "balance") %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature")),
         process = gsub("_", " ", process),
         test = factor(test, levels = c("neural signature", "ROI", "association", "uniformity"))) %>%
  ggplot(aes(control, value_std, fill = condition)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "bar", position = position_dodge(.9)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = position_dodge(.9), width = 0) +
  facet_wrap(~ test + process, nrow = 3) +
  scale_fill_manual(name = "", values = pal_condition) +
  labs(x = "\ncontrol condition", y = "mean standardized parameter estimate\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")
```

```{r, fig.width=12, fig.height=10}
combined_plot %>%
  filter(!process == "balance") %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature")),
         process = gsub("_", " ", process),
         process = ifelse(!test == "ROI", sprintf("%s PEV", process), sprintf("%s ROI", process)),
         test = ifelse(!test %in% c("association", "uniformity"), "none", test),
         test = factor(test, levels = c("none", "association", "uniformity"))) %>%
  ggplot(aes(control, value_std, fill = process)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "bar", position = position_dodge(.9)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = position_dodge(.9), width = 0) +
  facet_grid(test~condition) +
  scale_fill_manual(name = "", values = pal_condition8) +
  labs(x = "\ncontrol condition", y = "mean standardized parameter estimate\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")
```

## body composition plots {.tabset}
### ROIs
Mean parameter estimates as a function of process, stimulus type, and control condition

```{r, fig.width=8, fig.height=4.5}
betas_plot %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(condition, meanProcessPEstd, fill = control)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "bar", position = position_dodge(.9)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = position_dodge(.9), width = 0) +
  facet_grid(~process) +
  scale_fill_manual(name = "", values = pal_control) +
  labs(x = "\nstimulus", y = "mean standardized parameter estimate\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")

betas_plot %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(control, meanProcessPEstd, fill = condition)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "bar", position = position_dodge(.9)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = position_dodge(.9), width = 0) +
  facet_grid(~process) +
  scale_fill_manual(name = "", values = pal_condition) +
  labs(x = "\ncontrol condition", y = "mean standardized parameter estimate\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")
```

Correlations between variables and BMI or % fat
```{r, fig.width=10, fig.height=8}
betas_plot %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(bmi, meanProcessPEstd, color = condition)) +
  geom_point(alpha = .2) +
  geom_smooth(method = "lm", alpha = .25) +
  facet_grid(control~process) +
  scale_color_manual(name = "", values = pal_condition) +
  labs(x = "\nBMI", y = "mean standardized parameter estimate\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")

betas_plot %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(fat, meanProcessPEstd, color = condition)) +
  geom_point(alpha = .2) +
  geom_smooth(method = "lm", alpha = .25) +
  facet_grid(control~process) +
  scale_color_manual(name = "", values = pal_condition) +
  labs(x = "\nbody composition (% fat)", y = "mean standardized parameter estimate\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")
```

### PEVs
Mean correspondance as a function of process, stimulus type, control condition, and test

```{r, fig.width=10, fig.height=8}
dots_plot %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(condition, dotProduct_std, fill = control)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "bar", position = position_dodge(.9)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = position_dodge(.9), width = 0) +
  facet_grid(test~process) +
  scale_fill_manual(name = "", values = pal_control) +
  labs(x = "\nstimulus", y = "mean correspondance\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")

dots_plot %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(control, dotProduct_std, fill = condition)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "bar", position = position_dodge(.9)) +
  stat_summary(fun.data = "mean_cl_boot", geom = "errorbar", position = position_dodge(.9), width = 0) +
  facet_grid(test~process) +
  scale_fill_manual(name = "", values = pal_condition) +
  labs(x = "\ncontrol condition", y = "mean correspondance\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")
```

Correlations between variables and BMI or % fat
```{r, fig.width=12, fig.height=12}
dots_plot %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(bmi, dotProduct_std, color = condition)) +
  geom_point(alpha = .2) +
  geom_smooth(method = "lm", alpha = .25) +
  facet_grid(control + test ~ process) +
  scale_color_manual(name = "", values = pal_condition) +
  labs(x = "\nBMI", y = "mean standardized parameter estimate\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")

dots_plot %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(fat, dotProduct_std, color = condition)) +
  geom_point(alpha = .2) +
  geom_smooth(method = "lm", alpha = .25) +
  facet_grid(control + test ~ process) +
  scale_color_manual(name = "", values = pal_condition) +
  labs(x = "\nbody composition (% fat)", y = "mean standardized parameter estimate\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")
```

## EMA plots {.tabset}
### ROIs
```{r, fig.width=8, fig.height=5}
model_data_ema %>%
  select(subjectID, contains("ROI"), desire_pres0.prop, desire_str.m, goal_conf.m, resist.m, enact_prop, amount_Recoded.m) %>%
  unique() %>%
  gather(neuro_var, neuro_val, contains("ROI")) %>%
  mutate(neuro_var = factor(neuro_var, levels = c("balance_ROI", "cognitive_control_ROI",
                                                  "reward_ROI", "value_ROI"))) %>%
  gather(ema_var, ema_val, contains("m"), contains("prop")) %>%
  group_by(ema_var) %>%
  do({
    plot = ggplot(., aes(neuro_val, ema_val, color = neuro_var)) +
      geom_point(alpha = .5) +
      geom_smooth(method = "lm", alpha = .1, fullrange = TRUE) +
      scale_color_manual(name = "", values = pal_condition) +
      labs(x = "\n mean parameter estimate", y = paste0(.$ema_var[[1]], "\n")) +
      theme_minimal(base_size = 14)
    
    print(plot)
    data.frame()
  })
```

### PEVs
```{r, fig.width=8, fig.height=5}
model_data_ema %>%
  select(subjectID, contains("PEV"), desire_pres0.prop, desire_str.m, goal_conf.m, resist.m, enact_prop, amount_Recoded.m) %>%
  unique() %>%
  gather(neuro_var, neuro_val, contains("PEV")) %>%
  mutate(neuro_var = factor(neuro_var, levels = c("cognitive_control_PEV", "reward_PEV", "value_PEV",
                                                  "craving_PEV", "craving_regulation_PEV"))) %>%
  gather(ema_var, ema_val, contains("m"), contains("prop")) %>%
  group_by(ema_var) %>%
  do({
    plot = ggplot(., aes(neuro_val, ema_val, color = neuro_var)) +
      geom_point(alpha = .5) +
      geom_smooth(method = "lm", alpha = .1, fullrange = TRUE) +
      scale_color_manual(name = "", values = pal_condition[2:6]) +
      labs(x = "\n mean parameter estimate", y = paste0(.$ema_var[[1]], "\n")) +
      theme_minimal(base_size = 14)
    
    print(plot)
    data.frame()
  })

```

## correlations among ROIs and PEVs {.tabset}
```{r}
dots_plot %>%
  filter(!grepl("craving", process)) %>%
  left_join(., betas_plot) %>%
  mutate(condition = factor(condition, levels = c("food", "dessert", "meal", "snack", "social", "nature"))) %>%
  ggplot(aes(meanProcessPEstd, dotProduct_std, color = condition)) +
  geom_point(alpha = .2) +
  geom_smooth(method = "lm", alpha = .25) +
  facet_grid(control + test ~ process) +
  scale_color_manual(name = "", values = pal_condition) +
  labs(x = "\nmean standardized parameter estimate", y = "mean standardized PEV\n") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        legend.box = "horizontal")
```

### PEVs v ROIs
```{r, fig.width=14, fig.height=17}
dots_plot %>%
  unite(var, process, test, condition, control, sep = "_") %>%
  mutate(var = sprintf("dot_%s", var)) %>%
  spread(var, dotProduct_std) %>%
  left_join(., betas_plot) %>%
  unite(var, process, condition, control, sep = "_") %>%
  mutate(var = sprintf("roi_%s", var)) %>%
  spread(var, meanProcessPEstd) %>%
  select(-subjectID) %>%
  cor(., use = "pairwise.complete.obs") %>%
  reshape2::melt() %>%
  filter(!grepl("dot", Var1) & !grepl("roi", Var2)) %>%
  ggplot(aes(Var1, Var2, fill = value)) +
    geom_tile(color = "white") +
    scale_fill_gradientn(name = "correlation\n", colors = c(pal_condition[1], "white", pal_condition[6]), limits = c(-1, 1), breaks = c(-1, 0, 1)) + 
    geom_text(aes(label = round(value, 1)), size = 2) +
    labs(x = "", y = "") + 
    theme(legend.text = element_text(size = 8),
          legend.position = "top",
          legend.title = element_blank(),
          axis.text = element_text(color = "black"),
          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          axis.line = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
```

### ROIs
```{r, fig.width=10, fig.height=10}
dots_plot %>%
  unite(var, process, test, condition, control, sep = "_") %>%
  mutate(var = sprintf("dot_%s", var)) %>%
  spread(var, dotProduct_std) %>%
  left_join(., betas_plot) %>%
  unite(var, process, condition, control, sep = "_") %>%
  mutate(var = sprintf("roi_%s", var)) %>%
  spread(var, meanProcessPEstd) %>%
  select(-subjectID) %>%
  cor(., use = "pairwise.complete.obs") %>%
  reshape2::melt() %>%
  filter(grepl("roi", Var1) & grepl("roi", Var2)) %>%
  ggplot(aes(Var1, Var2, fill = value)) +
    geom_tile(color = "white") +
    scale_fill_gradientn(name = "correlation\n", colors = c(pal_condition[1], "white", pal_condition[6]), limits = c(-1, 1), breaks = c(-1, 0, 1)) + 
    geom_text(aes(label = round(value, 1)), size = 2) +
    labs(x = "", y = "") + 
    theme(legend.text = element_text(size = 8),
          legend.position = "top",
          legend.title = element_blank(),
          axis.text = element_text(color = "black"),
          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          axis.line = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())

```

### PEVs
```{r, fig.width=16, fig.height=16}
dots_plot %>%
  unite(var, process, test, condition, control, sep = "_") %>%
  mutate(var = sprintf("dot_%s", var)) %>%
  spread(var, dotProduct_std) %>%
  left_join(., betas_plot) %>%
  unite(var, process, condition, control, sep = "_") %>%
  mutate(var = sprintf("roi_%s", var)) %>%
  spread(var, meanProcessPEstd) %>%
  select(-subjectID) %>%
  cor(., use = "pairwise.complete.obs") %>%
  reshape2::melt() %>%
  filter(grepl("dot", Var1) & grepl("dot", Var2)) %>%
  ggplot(aes(Var1, Var2, fill = value)) +
    geom_tile(color = "white") +
    scale_fill_gradientn(name = "correlation\n", colors = c(pal_condition[1], "white", pal_condition[6]), limits = c(-1, 1), breaks = c(-1, 0, 1)) + 
    geom_text(aes(label = round(value, 1)), size = 2) +
    labs(x = "", y = "") + 
    theme(legend.text = element_text(size = 8),
          legend.position = "top",
          legend.title = element_blank(),
          axis.text = element_text(color = "black"),
          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          axis.line = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
```

# run cross-validated models
## descriptives
```{r}
model_data %>%
  left_join(., model_data_ema) %>%
  gather(Variable, val, contains("PEV"), contains("ROI"), bmi, fat, enact_prop) %>%
  filter(!Variable == "balance_ROI") %>%
  group_by(Variable) %>%
  summarize(M = mean(val, na.rm = TRUE),
            SD = sd(val, na.rm = TRUE)) %>%
  filter(!is.na(Variable)) %>%
  mutate(Variable = gsub("_", " ", Variable),
         Variable = ifelse(Variable == "bmi", "BMI",
                    ifelse(Variable == "fat", "Body fat percentage",
                    ifelse(Variable == "enact prop", "Enactment", Hmisc::capitalize(Variable)))),
         Variable = factor(Variable, levels = c("BMI", "Body fat percentage", "Enactment",
                                                "Reward ROI", "Reward PEV",
                                                "Value ROI", "Value PEV",
                                                "Craving regulation PEV", "Craving PEV",
                                                "Cognitive control ROI", "Cognitive control PEV"))) %>%
  arrange(Variable) %>%
  kable(format = "pandoc", digits = 2)

cor_mat = model_data %>%
  left_join(., model_data_ema) %>%
  select(bmi, fat, enact_prop, contains("ROI"), contains("PEV"), -balance_ROI) %>%
  gather(var, val, contains("PEV"), contains("ROI"), bmi, fat, enact_prop) %>%
  mutate(var = gsub("_", " ", var),
         var = ifelse(var == "bmi", "BMI",
               ifelse(var == "fat", "Body fat percentage",
               ifelse(var == "enact prop", "Enactment", Hmisc::capitalize(var)))),
         var = factor(var, levels = c("BMI", "Body fat percentage", "Enactment",
                                      "Reward ROI", "Reward PEV",
                                      "Value ROI", "Value PEV",
                                      "Craving regulation PEV", "Craving PEV",
                                      "Cognitive control ROI", "Cognitive control PEV"))) %>%
  arrange(var) %>%
  spread(var, val) %>%
  ungroup() %>%
  select(-subjectID) %>%
  as.matrix()

cors = Hmisc::rcorr(cor_mat)

cors$r %>%
  as.data.frame() %>%
  kable(format = "pandoc", digits = 2)

cors$P %>%
  as.data.frame() %>%
  mutate_if(is.numeric, funs(ifelse(between(., .05, .1), "†",
                             ifelse(between(., .01, .05), "*", 
                             ifelse(between(., .001, .01), "**",
                             ifelse(. < .001, "***", "")))))) %>%
  kable(format = "pandoc", digits = 2)
```

### t-tests
```{r}
model_data %>%
  select(-contains("z"), -balance_ROI) %>%
  left_join(., select(model_data_ema, subjectID, enact_prop)) %>%
  ungroup() %>%
  select_if(is.numeric) %>%
  map_df(~ broom::tidy(t.test(.x, mu = 0, na.action = "na.omit")), .id = "x") %>%
  rename("Variable" = x,
         "t" = statistic,
         "df" = parameter,
         "p" = p.value) %>%
  mutate(`Mdiff [95% CI]` = sprintf("%.02f [%.02f, %.02f]", estimate, conf.low, conf.high),
         p = ifelse(p < .001, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p))),
         Variable = gsub("enact_prop", "Enactment", Variable),
         Variable = gsub("fat", "Body fat percentage", Variable),
         Variable = gsub("bmi", "BMI", Variable),
         Variable = gsub("_", " ", Variable),
         Variable = factor(Variable, levels = c("BMI", "Body fat percentage", "Enactment",
                                                "reward ROI", "reward PEV",
                                                "value ROI", "value PEV",
                                                "craving regulation PEV", "craving PEV",
                                                "cognitive control ROI", "cognitive control PEV"))) %>%
  select(Variable, `Mdiff [95% CI]`, t, df, p) %>%
  arrange(Variable) %>%
  kable(format = "pandoc", digits = 2)
```

## specify model variables
```{r}
options(na.action = "na.fail")
data_ctrl = caret::trainControl(method = "repeatedcv", number = 5, repeats = 5)
```

## BMI {.tabset}
### ROI models
```{r}
bmi_roi_full = lm(bmi_z ~ value_ROI + reward_ROI + cognitive_control_ROI, data = model_data_bmi)
(bmi_roi_mods = MuMIn::dredge(bmi_roi_full))
```

```{r}
MuMIn::get.models(bmi_roi_mods, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest()

best_bmi_roi = caret::train(bmi_z ~ reward_ROI + value_ROI,
                     data = model_data_bmi,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
```

### PEV models
```{r}
bmi_pev_full = lm(bmi_z ~ value_PEV + reward_PEV + cognitive_control_PEV + craving_PEV + craving_regulation_PEV, data = model_data_bmi)
(bmi_pev_mods = MuMIn::dredge(bmi_pev_full))
```

```{r}
MuMIn::get.models(bmi_pev_mods, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest()

best_bmi_pev = caret::train(bmi_z ~ craving_regulation_PEV,
                     data = model_data_bmi,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
```

### combined
```{r}
bmi_null = lm(bmi_z ~ 1, data = model_data_bmi)
summary(bmi_null)

bmi_combined = caret::train(bmi_z ~ reward_ROI + value_ROI + craving_regulation_PEV,
                     data = model_data_bmi,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)

(bmi_aic = AIC(bmi_null, best_bmi_roi$finalModel, best_bmi_pev$finalModel, bmi_combined$finalModel) %>%
    rownames_to_column() %>%
    extract(rowname, "model", ".*bmi_(.*)\\$.*") %>%
    mutate(model = toupper(model),
           model = ifelse(is.na(model), "Null", model)) %>%
  arrange(AIC))
```

#### summarize the overall best fitting
```{r}
# ROI
summary(best_bmi_roi$finalModel)
best_bmi_roi
sd(best_bmi_roi$resample$Rsquared)
sd(best_bmi_roi$resample$RMSE)

# combined
summary(bmi_combined$finalModel)
bmi_combined
sd(bmi_combined$resample$Rsquared)
sd(bmi_combined$resample$RMSE)
```

## % fat {.tabset}
### ROI models
```{r}
fat_roi_full = lm(fat_z ~ value_ROI + reward_ROI + cognitive_control_ROI, data = model_data_fat)
(fat_roi_mods = MuMIn::dredge(fat_roi_full))
```

```{r}
MuMIn::get.models(fat_roi_mods, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest()

best_fat_roi = caret::train(fat_z ~ reward_ROI,
                     data = model_data_fat,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
```

### PEV models
```{r}
fat_pev_full = lm(fat_z ~ value_PEV + reward_PEV + cognitive_control_PEV + craving_PEV + craving_regulation_PEV, data = model_data_fat)
(fat_pev_mods = MuMIn::dredge(fat_pev_full))
```

```{r}
MuMIn::get.models(fat_pev_mods, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest()

best_fat_pev = caret::train(fat_z ~ craving_PEV,
                     data = model_data_fat,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
```

### combined
```{r}
fat_null = lm(fat_z ~ 1, data = model_data_fat)

fat_combined = caret::train(fat_z ~ reward_ROI + craving_PEV,
                     data = model_data_fat,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)

(fat_aic = AIC(fat_null, best_fat_roi$finalModel, best_fat_pev$finalModel, fat_combined$finalModel) %>%
    rownames_to_column() %>%
    extract(rowname, "model", ".*fat_(.*)\\$.*") %>%
    mutate(model = toupper(model),
           model = ifelse(is.na(model), "Null", model)) %>%
    arrange(AIC))
```

### summarize the overall best fitting
```{r}
summary(fat_null)
```


## EMA enactment proportion {.tabset}
### ROI models
```{r}
enact_prop_roi_full = lm(enact_prop_z ~ value_ROI + reward_ROI + cognitive_control_ROI, data = model_data_ema)
(enact_prop_roi_mods = MuMIn::dredge(enact_prop_roi_full))
```

```{r}
MuMIn::get.models(enact_prop_roi_mods, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest()

best_enact_prop_roi = caret::train(enact_prop_z ~ value_ROI,
                     data = model_data_ema,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
```

### PEV models
```{r}
enact_prop_pev_full = lm(enact_prop_z ~ value_PEV + reward_PEV + cognitive_control_PEV + craving_PEV + craving_regulation_PEV, data = model_data_ema)
(enact_prop_pev_mods = MuMIn::dredge(enact_prop_pev_full))
```

```{r}
MuMIn::get.models(enact_prop_pev_mods, subset = TRUE) %>%
  tibble() %>%
  rename("model" = ".") %>%
  mutate(tidied = purrr::map(model, broom::tidy),
         model_num = row_number()) %>%
  select(model_num, tidied) %>%
  unnest()

best_enact_prop_pev = caret::train(enact_prop_z ~ reward_PEV,
                     data = model_data_ema,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
```

### combined
```{r}
enact_prop_null = lm(enact_prop_z ~ 1, data = model_data_ema)

enact_prop_combined = caret::train(enact_prop_z ~ value_ROI + reward_PEV,
                     data = model_data_ema,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)

(enact_aic = AIC(enact_prop_null, best_enact_prop_roi$finalModel, best_enact_prop_pev$finalModel, enact_prop_combined$finalModel) %>%
    rownames_to_column() %>%
    extract(rowname, "model", ".*prop_(.*)\\$.*") %>%
    mutate(model = toupper(model),
           model = ifelse(is.na(model), "Null", model)) %>%
  arrange(AIC))

```

### summarize the overall best fitting
```{r}
summary(best_enact_prop_pev$finalModel)
best_enact_prop_pev
sd(best_enact_prop_pev$resample$Rsquared)
sd(best_enact_prop_pev$resample$RMSE)
```

# tables {.tabset}
## bmi
```{r}
bmi_fit = data.frame(model = c("ROI", "PEV", "COMBINED"),
                     r2 = c(mean(best_bmi_roi$resample$Rsquared), 
                            mean(best_bmi_pev$resample$Rsquared), 
                            mean(bmi_combined$resample$Rsquared)),
                     r2_sd = c(sd(best_bmi_roi$resample$Rsquared), 
                               sd(best_bmi_pev$resample$Rsquared), 
                               sd(bmi_combined$resample$Rsquared)),
                     RMSE = c(mean(best_bmi_roi$resample$RMSE), 
                              mean(best_bmi_pev$resample$RMSE), 
                              mean(bmi_combined$resample$RMSE)),
                     RMSE_sd = c(sd(best_bmi_roi$resample$RMSE), 
                                 sd(best_bmi_pev$resample$RMSE), 
                                 sd(bmi_combined$resample$RMSE)))

bmi_table = broom::tidy(best_bmi_roi$finalModel, conf.int = TRUE) %>% 
  mutate(model = "ROI", 
         mod_sig = ifelse(pf(summary(best_bmi_roi$finalModel)$fstatistic[1], 
                             summary(best_bmi_roi$finalModel)$fstatistic[2], 
                             summary(best_bmi_roi$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", "")) %>%
  bind_rows(broom::tidy(best_bmi_pev$finalModel, conf.int = TRUE) %>% 
              mutate(model = "PEV",
                     mod_sig = ifelse(pf(summary(best_bmi_pev$finalModel)$fstatistic[1], 
                             summary(best_bmi_pev$finalModel)$fstatistic[2], 
                             summary(best_bmi_pev$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(bmi_combined$finalModel, conf.int = TRUE) %>% 
              mutate(model = "COMBINED",
                     mod_sig = ifelse(pf(summary(bmi_combined$finalModel)$fstatistic[1], 
                             summary(bmi_combined$finalModel)$fstatistic[2], 
                             summary(bmi_combined$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(bmi_null, conf.int = TRUE) %>% mutate(model = "Null", mod_sig = "")) %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high),
         p = ifelse(p < .001, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p))),
         term = gsub("\\(Intercept\\)", "Intercept", term),
         term = gsub("_", " ", term),
         term = Hmisc::capitalize(term)) %>%
  left_join(., bmi_aic) %>%
  left_join(., bmi_fit) %>%
  mutate(`r2 (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", r2, r2_sd), "--"),
         `RMSE (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", RMSE, RMSE_sd), "--")) %>%
  unite(model, model, mod_sig, sep = "") %>%
  select(model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p) %>%
  arrange(AIC) %>%
  mutate(model = gsub("COMBINED", "Combined", model),
         outcome = "BMI") %>%
    select(outcome, model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p)

bmi_table %>%
  kable(format = "pandoc", digits = 2)
```

## % fat
```{r}
fat_fit = data.frame(model = c("ROI", "PEV", "COMBINED"),
                     r2 = c(mean(best_fat_roi$resample$Rsquared), 
                            mean(best_fat_pev$resample$Rsquared), 
                            mean(fat_combined$resample$Rsquared)),
                     r2_sd = c(sd(best_fat_roi$resample$Rsquared), 
                               sd(best_fat_pev$resample$Rsquared), 
                               sd(fat_combined$resample$Rsquared)),
                     RMSE = c(mean(best_fat_roi$resample$RMSE), 
                              mean(best_fat_pev$resample$RMSE), 
                              mean(fat_combined$resample$RMSE)),
                     RMSE_sd = c(sd(best_fat_roi$resample$RMSE), 
                                 sd(best_fat_pev$resample$RMSE), 
                                 sd(fat_combined$resample$RMSE)))

fat_table = broom::tidy(best_fat_roi$finalModel, conf.int = TRUE) %>% 
  mutate(model = "ROI", 
         mod_sig = ifelse(pf(summary(best_fat_roi$finalModel)$fstatistic[1], 
                             summary(best_fat_roi$finalModel)$fstatistic[2], 
                             summary(best_fat_roi$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", "")) %>%
  bind_rows(broom::tidy(best_fat_pev$finalModel, conf.int = TRUE) %>% 
              mutate(model = "PEV",
                     mod_sig = ifelse(pf(summary(best_fat_pev$finalModel)$fstatistic[1], 
                             summary(best_fat_pev$finalModel)$fstatistic[2], 
                             summary(best_fat_pev$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(fat_combined$finalModel, conf.int = TRUE) %>% 
              mutate(model = "COMBINED",
                     mod_sig = ifelse(pf(summary(fat_combined$finalModel)$fstatistic[1], 
                             summary(fat_combined$finalModel)$fstatistic[2], 
                             summary(fat_combined$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(fat_null, conf.int = TRUE) %>% mutate(model = "Null", mod_sig = "")) %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high),
         p = ifelse(p < .001, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p))),
         term = gsub("\\(Intercept\\)", "Intercept", term),
         term = gsub("_", " ", term),
         term = Hmisc::capitalize(term)) %>%
  left_join(., fat_aic) %>%
  left_join(., fat_fit) %>%
  mutate(`r2 (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", r2, r2_sd), "--"),
         `RMSE (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", RMSE, RMSE_sd), "--")) %>%
  unite(model, model, mod_sig, sep = "") %>%
  select(model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p) %>%
  arrange(AIC) %>%
  mutate(model = gsub("COMBINED", "Combined", model),
         outcome = "Body fat") %>%
    select(outcome, model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p)

fat_table %>%
  kable(format = "pandoc", digits = 2)
```

## EMA enactment
```{r}
enact_prop_fit = data.frame(model = c("ROI", "PEV", "COMBINED"),
                     r2 = c(mean(best_enact_prop_roi$resample$Rsquared), 
                            mean(best_enact_prop_pev$resample$Rsquared), 
                            mean(enact_prop_combined$resample$Rsquared)),
                     r2_sd = c(sd(best_enact_prop_roi$resample$Rsquared), 
                               sd(best_enact_prop_pev$resample$Rsquared), 
                               sd(enact_prop_combined$resample$Rsquared)),
                     RMSE = c(mean(best_enact_prop_roi$resample$RMSE), 
                              mean(best_enact_prop_pev$resample$RMSE), 
                              mean(enact_prop_combined$resample$RMSE)),
                     RMSE_sd = c(sd(best_enact_prop_roi$resample$RMSE), 
                                 sd(best_enact_prop_pev$resample$RMSE), 
                                 sd(enact_prop_combined$resample$RMSE)))

enact_table = broom::tidy(best_enact_prop_roi$finalModel, conf.int = TRUE) %>% 
  mutate(model = "ROI", 
         mod_sig = ifelse(pf(summary(best_enact_prop_roi$finalModel)$fstatistic[1], 
                             summary(best_enact_prop_roi$finalModel)$fstatistic[2], 
                             summary(best_enact_prop_roi$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", "")) %>%
  bind_rows(broom::tidy(best_enact_prop_pev$finalModel, conf.int = TRUE) %>% 
              mutate(model = "PEV",
                     mod_sig = ifelse(pf(summary(best_enact_prop_pev$finalModel)$fstatistic[1], 
                             summary(best_enact_prop_pev$finalModel)$fstatistic[2], 
                             summary(best_enact_prop_pev$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(enact_prop_combined$finalModel, conf.int = TRUE) %>% 
              mutate(model = "COMBINED",
                     mod_sig = ifelse(pf(summary(enact_prop_combined$finalModel)$fstatistic[1], 
                             summary(enact_prop_combined$finalModel)$fstatistic[2], 
                             summary(enact_prop_combined$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(enact_prop_null, conf.int = TRUE) %>% mutate(model = "Null", mod_sig = "")) %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high),
         p = ifelse(p < .001, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p))),
         term = gsub("\\(Intercept\\)", "Intercept", term),
         term = gsub("_", " ", term),
         term = Hmisc::capitalize(term)) %>%
  left_join(., enact_aic) %>%
  left_join(., enact_prop_fit) %>%
  mutate(`r2 (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", r2, r2_sd), "--"),
         `RMSE (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", RMSE, RMSE_sd), "--")) %>%
  unite(model, model, mod_sig, sep = "") %>%
  select(model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p) %>%
  arrange(AIC) %>%
  mutate(model = gsub("COMBINED", "Combined", model),
         outcome = "Enactment") %>%
    select(outcome, model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p)

enact_table %>%
  kable(format = "pandoc", digits = 2)
```

## combined
```{r}
bind_rows(bmi_table, fat_table, enact_table) %>%
  kable(format = "pandoc", digits = 2)
```

# VIF
```{r}
# BMI
car::vif(bmi_combined$finalModel)

# %fat
car::vif(fat_combined$finalModel)

# enactment
car::vif(enact_prop_combined$finalModel)
```
