---
title: "Supplementary Cross-validated Model Comparison"
author: "Dani Cosme & Rich Lopez"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = FALSE, fig.path = "figs/prediction_supp/")
```

# load packages
```{r}
library(tidyverse)
library(knitr)
```

# define palettes
```{r}
pal_control = c("#2E86B4", "#F2B827")
pal_outcome = wesanderson::wes_palette("Zissou1", 3, "continuous")
pal_ind = wesanderson::wes_palette("Zissou1", 4, "continuous")
pal_condition = wesanderson::wes_palette("Zissou1", 6, "continuous")
pal_condition8 = wesanderson::wes_palette("Zissou1", 16, "continuous")
pal_condition8 = c(pal_condition8[1], pal_condition8[3],
                  pal_condition8[14], pal_condition8[5],
                  pal_condition8[15], pal_condition8[16],
                  pal_condition8[9], pal_condition8[12])
```

# load data
* code sex as -.5 (female), .5 (male)
```{r, cache=TRUE}
ind_diffs = readRDS("ind_diffs.RDS") %>%
  mutate(restraint_z = as.numeric(scale(restraint)),
         sex = ifelse(gender == 1, -.5,
                  ifelse(gender == 2, .5, gender))) %>%
  select(subjectID, sample, sex, age, restraint, restraint_z)


dataset = readRDS("full_dataset.RDS") %>% select(-age, -gender)
ema = readRDS("ema.RDS")
betas_std = readRDS("betas_dataset.RDS")
dots_std = readRDS("dots_dataset.RDS")
```

## tidy data for modeling
```{r}
ema_tidy = ema %>%
  select(subjectID, enact_prop) %>%
  unique() %>%
  filter(!is.na(subjectID)) %>%
  mutate(enact_prop_z = as.numeric(scale(enact_prop)))

model_data = dataset %>%
  filter(test == "association" & mask == "unmasked" & session == "all" & control == "nature" & condition == "food") %>%
  unique() %>%
  group_by(process, subjectID) %>%
  mutate(meanProcessPEstd = mean(meanPE_std, na.rm = TRUE),
         processPE = paste0(process, "_ROI"),
         processPEV = paste0(process, "_PEV")) %>%
  ungroup() %>%
  select(-c(xyz, meanPE, meanPE_std, sdPE, dotProduct, map, process)) %>%
  spread(processPEV, dotProduct_std) %>%
  spread(processPE, meanProcessPEstd) %>%
  group_by(subjectID) %>%
  fill(contains("PEV"), .direction = "down") %>%
  fill(contains("PEV"), .direction = "up") %>%
  fill(contains("ROI"), .direction = "down") %>%
  fill(contains("ROI"), .direction = "up") %>%
  select(-c(roi, craving_ROI, craving_regulation_ROI, test, mask)) %>%
  unique() %>%
  left_join(., ind_diffs)

model_data_bmi = model_data %>%
  select(-contains("fat")) %>%
  na.omit()

model_data_fat = model_data %>%
  select(-contains("bmi")) %>%
  na.omit()

model_data_ema = model_data %>%
  select(-contains("fat"), -contains("bmi")) %>%
  right_join(., ema_tidy, by = "subjectID") %>%
  na.omit()
```

# run cross-validated models
## specify model variables
```{r}
options(na.action = "na.fail")
data_ctrl = caret::trainControl(method = "repeatedcv", number = 5, repeats = 5)
set.seed(123)
```

## BMI {.tabset}
* add sex and dietary restraint covariates to the best fitting models

```{r}
# ROI model
best_bmi_roi = caret::train(bmi_z ~ reward_ROI + value_ROI + sex + restraint,
                     data = model_data_bmi,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)

# PEV model
best_bmi_pev = caret::train(bmi_z ~ craving_regulation_PEV + sex + restraint,
                     data = model_data_bmi,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
# combined
bmi_null = lm(bmi_z ~ 1 + sex + restraint, data = model_data_bmi)

bmi_combined = caret::train(bmi_z ~ reward_ROI + value_ROI + craving_regulation_PEV + sex + restraint,
                     data = model_data_bmi,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)

(bmi_aic = AIC(bmi_null, best_bmi_roi$finalModel, best_bmi_pev$finalModel, bmi_combined$finalModel) %>%
    rownames_to_column() %>%
    extract(rowname, "model", ".*bmi_(.*)\\$.*") %>%
    mutate(model = toupper(model),
           model = ifelse(is.na(model), "Null", model)) %>%
  arrange(AIC))
```

## % fat
```{r}
# ROI model
best_fat_roi = caret::train(fat_z ~ reward_ROI + sex + restraint,
                     data = model_data_fat,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
# PEV model
best_fat_pev = caret::train(fat_z ~ craving_PEV + sex + restraint,
                     data = model_data_fat,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
# combined
fat_null = lm(fat_z ~ 1 + sex + restraint, data = model_data_fat)

fat_combined = caret::train(fat_z ~ reward_ROI + craving_PEV + sex + restraint,
                     data = model_data_fat,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)

(fat_aic = AIC(fat_null, best_fat_roi$finalModel, best_fat_pev$finalModel, fat_combined$finalModel) %>%
    rownames_to_column() %>%
    extract(rowname, "model", ".*fat_(.*)\\$.*") %>%
    mutate(model = toupper(model),
           model = ifelse(is.na(model), "Null", model)) %>%
    arrange(AIC))
```

## EMA enactment proportion
* sex is not included in these models because the sample was all female

```{r}
# ROI model
best_enact_prop_roi = caret::train(enact_prop_z ~ value_ROI + restraint,
                     data = model_data_ema,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
# PEV models
best_enact_prop_pev = caret::train(enact_prop_z ~ reward_PEV + restraint,
                     data = model_data_ema,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)
# combined
enact_prop_null = lm(enact_prop_z ~ 1 + restraint, data = model_data_ema)

enact_prop_combined = caret::train(enact_prop_z ~ value_ROI + reward_PEV + restraint,
                     data = model_data_ema,
                     trControl = data_ctrl,
                     method = "lm",
                     na.action = na.omit)

(enact_aic = AIC(enact_prop_null, best_enact_prop_roi$finalModel, best_enact_prop_pev$finalModel, enact_prop_combined$finalModel) %>%
    rownames_to_column() %>%
    extract(rowname, "model", ".*prop_(.*)\\$.*") %>%
    mutate(model = toupper(model),
           model = ifelse(is.na(model), "Null", model)) %>%
  arrange(AIC))

```

# tables {.tabset}
## bmi
```{r}
bmi_fit = data.frame(model = c("ROI", "PEV", "COMBINED"),
                     r2 = c(mean(best_bmi_roi$resample$Rsquared), 
                            mean(best_bmi_pev$resample$Rsquared), 
                            mean(bmi_combined$resample$Rsquared)),
                     r2_sd = c(sd(best_bmi_roi$resample$Rsquared), 
                               sd(best_bmi_pev$resample$Rsquared), 
                               sd(bmi_combined$resample$Rsquared)),
                     RMSE = c(mean(best_bmi_roi$resample$RMSE), 
                              mean(best_bmi_pev$resample$RMSE), 
                              mean(bmi_combined$resample$RMSE)),
                     RMSE_sd = c(sd(best_bmi_roi$resample$RMSE), 
                                 sd(best_bmi_pev$resample$RMSE), 
                                 sd(bmi_combined$resample$RMSE)))

bmi_table = broom::tidy(best_bmi_roi$finalModel, conf.int = TRUE) %>% 
  mutate(model = "ROI", 
         mod_sig = ifelse(pf(summary(best_bmi_roi$finalModel)$fstatistic[1], 
                             summary(best_bmi_roi$finalModel)$fstatistic[2], 
                             summary(best_bmi_roi$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", "")) %>%
  bind_rows(broom::tidy(best_bmi_pev$finalModel, conf.int = TRUE) %>% 
              mutate(model = "PEV",
                     mod_sig = ifelse(pf(summary(best_bmi_pev$finalModel)$fstatistic[1], 
                             summary(best_bmi_pev$finalModel)$fstatistic[2], 
                             summary(best_bmi_pev$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(bmi_combined$finalModel, conf.int = TRUE) %>% 
              mutate(model = "COMBINED",
                     mod_sig = ifelse(pf(summary(bmi_combined$finalModel)$fstatistic[1], 
                             summary(bmi_combined$finalModel)$fstatistic[2], 
                             summary(bmi_combined$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(bmi_null, conf.int = TRUE) %>% mutate(model = "Null", mod_sig = "")) %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high),
         p = ifelse(p < .001, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p))),
         term = gsub("\\(Intercept\\)", "Intercept", term),
         term = gsub("_", " ", term),
         term = gsub("z", "", term),
         term = gsub("restraint", "dietary restraint", term),
         term = Hmisc::capitalize(term)) %>%
  left_join(., bmi_aic) %>%
  left_join(., bmi_fit) %>%
  mutate(`r2 (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", r2, r2_sd), "--"),
         `RMSE (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", RMSE, RMSE_sd), "--")) %>%
  unite(model, model, mod_sig, sep = "") %>%
  select(model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p) %>%
  arrange(AIC) %>%
  mutate(model = gsub("COMBINED", "Combined", model),
         outcome = "BMI") %>%
    select(outcome, model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p)

bmi_table %>%
  kable(format = "pandoc", digits = 2)
```

## % fat
```{r}
fat_fit = data.frame(model = c("ROI", "PEV", "COMBINED"),
                     r2 = c(mean(best_fat_roi$resample$Rsquared), 
                            mean(best_fat_pev$resample$Rsquared), 
                            mean(fat_combined$resample$Rsquared)),
                     r2_sd = c(sd(best_fat_roi$resample$Rsquared), 
                               sd(best_fat_pev$resample$Rsquared), 
                               sd(fat_combined$resample$Rsquared)),
                     RMSE = c(mean(best_fat_roi$resample$RMSE), 
                              mean(best_fat_pev$resample$RMSE), 
                              mean(fat_combined$resample$RMSE)),
                     RMSE_sd = c(sd(best_fat_roi$resample$RMSE), 
                                 sd(best_fat_pev$resample$RMSE), 
                                 sd(fat_combined$resample$RMSE)))

fat_table = broom::tidy(best_fat_roi$finalModel, conf.int = TRUE) %>% 
  mutate(model = "ROI", 
         mod_sig = ifelse(pf(summary(best_fat_roi$finalModel)$fstatistic[1], 
                             summary(best_fat_roi$finalModel)$fstatistic[2], 
                             summary(best_fat_roi$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", "")) %>%
  bind_rows(broom::tidy(best_fat_pev$finalModel, conf.int = TRUE) %>% 
              mutate(model = "PEV",
                     mod_sig = ifelse(pf(summary(best_fat_pev$finalModel)$fstatistic[1], 
                             summary(best_fat_pev$finalModel)$fstatistic[2], 
                             summary(best_fat_pev$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(fat_combined$finalModel, conf.int = TRUE) %>% 
              mutate(model = "COMBINED",
                     mod_sig = ifelse(pf(summary(fat_combined$finalModel)$fstatistic[1], 
                             summary(fat_combined$finalModel)$fstatistic[2], 
                             summary(fat_combined$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(fat_null, conf.int = TRUE) %>% mutate(model = "Null", mod_sig = "")) %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high),
         p = ifelse(p < .001, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p))),
         term = gsub("\\(Intercept\\)", "Intercept", term),
         term = gsub("_", " ", term),
         term = gsub("z", "", term),
         term = gsub("restraint", "dietary restraint", term),
         term = Hmisc::capitalize(term)) %>%
  left_join(., fat_aic) %>%
  left_join(., fat_fit) %>%
  mutate(`r2 (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", r2, r2_sd), "--"),
         `RMSE (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", RMSE, RMSE_sd), "--")) %>%
  unite(model, model, mod_sig, sep = "") %>%
  select(model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p) %>%
  arrange(AIC) %>%
  mutate(model = gsub("COMBINED", "Combined", model),
         outcome = "Body fat") %>%
    select(outcome, model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p)

fat_table %>%
  kable(format = "pandoc", digits = 2)
```

## EMA enactment
```{r}
enact_prop_fit = data.frame(model = c("ROI", "PEV", "COMBINED"),
                     r2 = c(mean(best_enact_prop_roi$resample$Rsquared), 
                            mean(best_enact_prop_pev$resample$Rsquared), 
                            mean(enact_prop_combined$resample$Rsquared)),
                     r2_sd = c(sd(best_enact_prop_roi$resample$Rsquared), 
                               sd(best_enact_prop_pev$resample$Rsquared), 
                               sd(enact_prop_combined$resample$Rsquared)),
                     RMSE = c(mean(best_enact_prop_roi$resample$RMSE), 
                              mean(best_enact_prop_pev$resample$RMSE), 
                              mean(enact_prop_combined$resample$RMSE)),
                     RMSE_sd = c(sd(best_enact_prop_roi$resample$RMSE), 
                                 sd(best_enact_prop_pev$resample$RMSE), 
                                 sd(enact_prop_combined$resample$RMSE)))

enact_table = broom::tidy(best_enact_prop_roi$finalModel, conf.int = TRUE) %>% 
  mutate(model = "ROI", 
         mod_sig = ifelse(pf(summary(best_enact_prop_roi$finalModel)$fstatistic[1], 
                             summary(best_enact_prop_roi$finalModel)$fstatistic[2], 
                             summary(best_enact_prop_roi$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", "")) %>%
  bind_rows(broom::tidy(best_enact_prop_pev$finalModel, conf.int = TRUE) %>% 
              mutate(model = "PEV",
                     mod_sig = ifelse(pf(summary(best_enact_prop_pev$finalModel)$fstatistic[1], 
                             summary(best_enact_prop_pev$finalModel)$fstatistic[2], 
                             summary(best_enact_prop_pev$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(enact_prop_combined$finalModel, conf.int = TRUE) %>% 
              mutate(model = "COMBINED",
                     mod_sig = ifelse(pf(summary(enact_prop_combined$finalModel)$fstatistic[1], 
                             summary(enact_prop_combined$finalModel)$fstatistic[2], 
                             summary(enact_prop_combined$finalModel)$fstatistic[3], lower = FALSE) < .05, "*", ""))) %>%
  bind_rows(broom::tidy(enact_prop_null, conf.int = TRUE) %>% mutate(model = "Null", mod_sig = "")) %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high),
         p = ifelse(p < .001, "< .001", gsub("0.(.*)", ".\\1", sprintf("%.3f", p))),
         term = gsub("\\(Intercept\\)", "Intercept", term),
         term = gsub("_", " ", term),
         term = gsub("z", "", term),
         term = gsub("restraint", "dietary restraint", term),
         term = Hmisc::capitalize(term)) %>%
  left_join(., enact_aic) %>%
  left_join(., enact_prop_fit) %>%
  mutate(`r2 (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", r2, r2_sd), "--"),
         `RMSE (SD)` = ifelse(!model == "Null", sprintf("%.2f (%.2f)", RMSE, RMSE_sd), "--")) %>%
  unite(model, model, mod_sig, sep = "") %>%
  select(model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p) %>%
  arrange(AIC) %>%
  mutate(model = gsub("COMBINED", "Combined", model),
         outcome = "Enactment") %>%
    select(outcome, model, AIC, `r2 (SD)`, `RMSE (SD)`, term, `b [95% CI]`, SE, t, p)

enact_table %>%
  kable(format = "pandoc", digits = 2)
```

## combined
```{r}
bind_rows(bmi_table, fat_table, enact_table) %>%
  kable(format = "pandoc", digits = 2)
```

# VIF
```{r}
# BMI
car::vif(bmi_combined$finalModel)

# %fat
car::vif(fat_combined$finalModel)

# enactment
car::vif(enact_prop_combined$finalModel)
```
